Micromechanism of Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with void

### 2019-01-09 Source/draft/wmm2.tex
Published

Poor ductility of Ti-Al alloy at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}. Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.  Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals (PTC)\cite{Appel2016}. Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}. A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}. 

>>>>

Poor ductility of Ti-Al alloy at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}. Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.  Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals (PTC)\cite{Appel2016}. Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}. Numerous studies cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}. 
